Performing graph-based clustering with rOpenScPCA

### 2024-12-13 analyses/hello-clusters/01_perform-evaluate-clustering.Rmd
Apply suggestions from code review
Co-authored-by: Joshua Shapiro <josh.shapiro@ccdatalab.org>

We'll also extract its PCA matrix, which we'll use to demonstrate how to calculate and evaluate clusters.
We'll show how to do this for both SCE and Seurat objects:

@@

@@

Even if you perform clustering with other tools, you can still use the `rOpenScPCA` functions to evaluate your clusters.

@@

```{r prepare scpca data frame}
scpca_cluster_df <- data.frame(
  cell_id = colnames(sce),
  cluster = colData(sce)$cluster
)

@@

```{r rename columns}
# First, rename columns in `cluster_results_df` to avoid ambiguity
cluster_results_renamed_df <- cluster_results_df |>
  # add the prefix openscpca_ to all columns
  dplyr::rename_with(~ paste0("ropenscpca_", .x))

>>>>

For the initial cluster calculations and evaluations, we will use the PCA matrix extracted from the SCE object.
It's also possible to use an SCE object or a Seurat object directly, which we will demonstrate later.
We'll show how to do this for both SCE and Seurat objects:

@@

# Print the first rows of the resulting table
head(cluster_results_df)
```

@@

If you already have clustering results calculated with other tools, you can still use the `rOpenScPCA` functions to evaluate your clusters.

@@

```{r prepare scpca data frame}
scpca_cluster_df <- data.frame(
  cell_id = colnames(sce),
  cluster = sce$cluster
)

@@

```{r rename columns}
# First, rename columns in `cluster_results_df` to avoid ambiguity
cluster_results_renamed_df <- cluster_results_df |>
  # add the prefix "ropenscpca_" to all columns
  dplyr::rename_with(\(x) paste0("ropenscpca_", x))
